%-------------------------
% Resume in Latex
% Author : Ajay R
% License : Open
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}	

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Ajay Command
\newcommand{\resumePPItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
%Ajay Command
\newcommand{\resumePPSubItem}[2]{\resumePPItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\blank}[1]{\hspace*{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Ajay Ramesh}} & Email : \href{mailto:ajayr.ec07@gmail.com}{ajayr.ec07@gmail.com}\\
  \href{https://www.linkedin.com/in/ajay-ramesh-kumar/}{linkedin.com/in/ajay-ramesh-kumar/} & Mobile : +91-8277419820 \\
\end{tabular*}

\section{Professional Profile}

%Commented section-------------------------------------------
\iffalse
{Skilled Engineer with a zest for a challenging work environment with high degree of
responsibility. Highly 
flexible in adjusting work pace to meet evolving client needs.}
\fi
%Commented section-------------------------------------------
\resumeSubHeadingListStart
    \resumePPSubItem{}{Embedded Software Engineer with 2+ years of experience in development and validation of Automotive Software.}
    \resumePPSubItem{}{Adept in C, VHDL and Assembly programming. Inquisitive Automation enthusiast in Python and Perl scripting. }
    \resumePPSubItem{}{Good knowledge about ARM7 architecture. Seeking to use extensive skills in Designing Verification testcases. }
    %\resumePPSubItem{}{}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Robert Bosch Engineering and Business Solutions}{Bangalore, India}
      {Embedded Software Engineer}{Jul 2016 - Present}
      \resumeItemListStart
        \item\small{Involved in development of automotive software for Engine Management System.\vspace{-2pt}}
        \item\small{Responsible for configuration and integration of AUTOSAR modules. \vspace{-2pt}}
		\iffalse
        \item\small{Responsible for customer requirements analysis for AUTOSAR adapter. \vspace{-2pt}}
		%\item\small{Handling and tracking System requirements (Issue SW)\vspace{-2pt}} 
		\item\small{Coordination of System \& SW requirements between customer project and customer platform. \vspace{-2pt}}
		\item\small{Carrying out System \& SW implementation review with function development. \vspace{-2pt}} 
        %\item{}\small{Integration of various functional components to build a complete software.\vspace{-2pt}}
        \fi
        \item\small{Involved in the development of test cases for Software verification and validation.}
		\item\small{Software Adapter development using Auto-Code Generation tools (ASCET).\vspace{-2pt}}
		\item\small{Embedded Software Validation and debugging(UDE) on the ECU via an emulation platform.\vspace{-2pt}}
		\item\small{\textbf{Key achievement} : Received good appreciation from the customer for debugging numerous critical issues.}
		
      \resumeItemListEnd

      \textit{Automation Engineer}\vspace{-5pt}
      \resumeItemListStart
		\item\small{Responsible for fully automated Continuous build and deployment infrastructure for multiple projects.\vspace{-2pt}}
		\item\small{Configuration using tools like Jenkins, Artifactory, GIT, SVN and other configuration management tools.\vspace{-2pt}}
		\item\small{Responsible for Automation of AUTOSAR Module Development/Integration using Perl, JS, Batch Scripting.\vspace{-2pt}}
		%\item{Designing, implementing and supporting fully automated Continuous Integration and Continuous Delivery processes.}
		\item\small{Involved in configuration of TestBench and execution of Automated Testing in Jenkins.\vspace{-2pt}}
		\item\small{\textbf{Key achievement} : Improved the overall productivity of the entire team by nearly 10$\%$.\vspace{-2pt}}
      \resumeItemListEnd

    \resumeSubheading
      {Fluxgen Technologies Ltd}{Bangalore, India}
      {Summer Intern}{May 2015 - July 2015}
      \resumeItemListStart
        \item\small{Developed embedded HW \& SW prototypes for Home Automation.\vspace{-2pt}}
		\item\small{Interfaced Temperature, Motion, Combustion sensors to a micro-controller.\vspace{-2pt}}
		\item\small{Deployed in an office and the data was logged into SD card for data analysis.\vspace{-2pt}}
		\item\small{Developed a module to calculate power consumption of all appliances.\vspace{-2pt}}
        \item\small{Plotted Voltage Waveforms in MATLAB for Real-Time Visualization. \vspace{-2pt}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology Karnataka}{Surathkal, India}
      {B.Tech in Electronics \& Communication}{2012 - 2016}\\ \vspace{5pt}
      %\resumeSubItem{GPA}{7.01}
     % {\small Courses : VLSI Design, Digital System Design, %Microprocessors, Digital signal processing \\ Advanced %Computer Architecture, Control Systems, Linear Systems and Signals. }
    \iffalse
    \resumeSubheading
      {Vidya Mandir P.U College}{Bangalore, India}
      {12th, PCMB}{2010 - 2012}
	\resumeSubheading
	  {M.E.S. Kishore Kendra}{Bangalore, India}
	  {10$^{th}$, High School}{2007 - 2010}
	\fi  
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{Tetris Game using Nexys 4 (FPGA)}
      {Emulated on a FPGA board with a VGA monitor using Xilinx.}
  \resumeSubItem{Recognizing hand-written digits}
	  {A Simple SVM classifier was implemented using Sklearn Py Modules.}
  \resumeSubItem{Arduino Radar}{Designed a Mini-Radar which detects objects around 8-10m circumferrence.}
  \resumeSubItem{Music Composer (DSK C6713)}
  {Generatation of discrete sinusoids of musical notes using the sampling frequency.}
  \resumeSubItem{Deep learning with OpenCL}
  {Implemented MNIST Neural Network using parallel computing algorithms in OpenCL.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
      \resumeSubItem{Programming}{: C, Python, Perl, VHDL, MATLAB, ARM programming}
      \resumeSubItem{Protocols}{:  CAN, SPI, I2C}
      \resumeSubItem{Softwares}{:  Xilinx, Eclipse, LtSpice, Code Composer Studio}
      %\resumeSubItem{Requirement Management}{: ClearQuest, RequestOne, ALM}
      \resumeSubItem{Languages}{:  English (Fluent), French (Beginner), German (Beginner) Kannada (Native)}
  \resumeSubHeadingListEnd

%-------------------------------------------


\end{document}